---
title: "R Sheet"
output: html_document
date: '`r Sys.Date()`'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#R Reference Sheet

##Loading Packages

For most work that you do, the `tidyverse` and `readxl` packages are the only ones that you will need. More packages are available, but these are your work horses. `tidyverse` gives you a bunch of data manipulation tools... super powerful. `readxl` allows you to read in excel files. Here is how you load them. Use `CTL + ENTER` with the code you want to run highlighted. You can also hit `CTL + ENTER` with your cursor at the end of a line to run that particular line of code. 

```{r}

library(readxl)
library(tidyverse)

```

##Working Directory and Loading Data

###Setting a working directory

Setting a working directory is not required, but it makes things easier. It makes your calls for loading files shorter.

```{r}
setwd("C:/Users/kbern/Documents/repos/Names/baby_data")

```

###Loading Data

Load the `baby_data.csv` data into an object called `baby_df`. You can call this literally whatever you want. Point being, there is an object called `baby_df` that is our data frame.

- `baby_df` is the object name
- `<-` means "assign to object"
- `read.csv()` is a function that loads in .csv data. It has the arguments:
-- `file` specifies the file you want to load, Remmeber the file extension. 
--`stringsAsFactors` do you want to load strings as factors? I always put this to false. 

```{r}
#this assumes you have your working directory set.
baby_df <- read.csv(file = "baby_data.csv", stringsAsFactors = FALSE)

#this is the same as the above command if you didn't have your working directory set. This is the long way of doing it. 

baby_df <- read.csv(file = "C:/Users/kbern/Documents/repos/Names/baby_data/baby_data.csv", stringsAsFactors = FALSE)

#if you wanted to load in an excel file, use the following:

#baby_df <- read_xlsx("baby_data.xlsx", sheet = "Sheet1")

```

After you run this, you will see the dataset in your "Environment" on the upper right side window. If you want to see your data, do the following. 

```{r}
View(baby_df)
```

You can get a pop-out of the data by clicking the "View in New Window" button next to the "Filter" button. 

Tadaaaa you lodaded in data!

## Basic Data Manipulation

### Filtering Data

I want to filter out only the rows that are designated as "Diaper". Store the resulting filtered data in a new object (`diaper_df`).

```{r}
diaper_df <- baby_df %>% filter(Type == "Diaper")
```

